---
title: "Multi DEG with RNAseqChef v1.1.4"
date: '`r format(Sys.time(), "%y/%m/%d %H:%M")`'
params:
    raw_count: [some object]
    input: [some object]
    multi_norm_count_matrix: [some object]
    multi_metadata: [some object]
    multi_umap_plot: [some object]
    multi_boxplot_reactive: [some object]
    multi_enrich_div_table: [some object]
    multi_kmeans_box: [some object]
    multi_enrich_k_table: [some object]
    multi_GSEA_table: [some object]
    multi_pattern1: [some object]
    multi_deg_count1: [some object]
output:
  word_document
fontsize: 10pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Parameters
 - Uploaded file name:
 
```{r echo = FALSE, results='asis'}
if(params$input$multi_data_file_type == "Row1" && !is.null(params$input$multi_file1)) {
  try(cat(paste0("raw_count_data: **", params$input$multi_file1$name,"**\n\n")))
}
if(params$input$multi_data_file_type == "Row2" && !is.null(params$input$multi_file2)) {
  try(cat(paste0("raw_count_data: **", params$input$multi_file2$name,"**\n\n")))
}
```

```{r echo = FALSE, results='asis'}
if(params$input$multi_data_file_type == "Row2" && !is.null(params$input$multi_file3)) {
  try(cat(paste0("metadata: **",params$input$multi_file3$name,"**\n\n")))
  try(knitr::kable(params$multi_metadata))
  cat("\n\n")
}
```
  
 
 - Experimental condition: 
```{r echo = FALSE, results='asis'}
label <- unique(gsub("\\_.+$", "", colnames(params$raw_count)))
for(i in 1:length(label)){
  cat(paste0("**",label[i],"**"))
  if(length(label) != i) cat(" **vs** ")
}
```

 - Method for DEG detection: 
 **DESeq2**
  - Method for FDR control: 
 **`r params$input$FDR_method6`**
 - Species: 
 **`r params$input$Species6`**
```{r echo = FALSE, results='asis'}
if(sum(is.element(no_orgDb, params$input$Species6)) == 1){
  try(cat(paste0("\nOrtholog: **", params$input$Ortholog6,"**\n\n")))
  try(cat(paste0("Host: **", params$input$Biomart_archive6,"**\n\n")))
}
```

 - Cut-off condition: 
 FoldChange = **`r params$input$fc6`**, FDR = **`r params$input$fdr6`**, 
 Basemean = **`r params$input$basemean6`**
 - tested raw count data
```{r echo = FALSE}
knitr::kable(head(params$raw_count))
```

 - Option: uploaded normalized count data: 
```{r echo = FALSE}
if(!is.null(params$input$multi_norm_file1)){
  knitr::kable(head(params$multi_norm_count_matrix))
}else print("no upload")
```

\newpage

##  Result overview

 - Clustering analysis (PCA, MDA, dendrogram (ward. D2)) (Clustering/clustering.pdf)

```{r, out.width="0.3\\linewidth", include=TRUE, fig.align="center", echo=FALSE}
try(magick::image_read_pdf("./Clustering/clustering.pdf"))
```

 - UMAP (Clustering/umap.pdf)
 
```{r, out.width="0.3\\linewidth", include=TRUE, fig.align="center", echo=FALSE}
if(length(params$multi_umap_plot) != 1){
try(magick::image_read_pdf("./Clustering/umap.pdf"))
}else print("Not performed")
```

 - table data
    - DEG_result (DEG_result/DEG_result.txt)
    - Normalized_count_data (DEG_result/normalized_count.txt)
    - PCA_table (Clustering/pca.txt)

\newpage

## Divisive clustering

 - Pair for fold change cut-off: 
**`r paste0(as.character(params$input$selectFC[1]),"_vs_",as.character(params$input$selectFC[2]))`**
 - Option: Pair for fold change cut-off: 
**`r paste0(as.character(params$input$selectFC_2[1]),"_vs_",as.character(params$input$selectFC_2[2]))`**
 - The DEG number after the filtration: **`r length(params$multi_pattern1$gene)`**
 - Tested gene number:
```{r echo = FALSE, results='asis'}
num <- length(params$multi_pattern1$gene)
if(!is.null(num)){
  if(!is.null(params$input$topP)){
    if(num < params$input$topP) cat(paste0("**",num, "**\n\n")) else cat(paste0("**",params$input$topP, "**\n\n"))
  }
}else print("Not performed")
```  


Summary boxplot: `r paste0("Divisive clustering_",as.character(params$input$selectFC[1]),"_vs_",as.character(params$input$selectFC[2]),"/Divisive_boxplot.pdf")`
 
```{r, out.width="0.3\\linewidth", include=TRUE, fig.align="center", echo=FALSE}
if(!is.null(params$multi_boxplot_reactive) && length(params$input$selectFC) == 2){
try(magick::image_read_pdf(paste0("Divisive clustering_",as.character(params$input$selectFC[1]),"_vs_",as.character(params$input$selectFC[2]),"/Divisive_boxplot.pdf")))
}else print("Not performed")
```

selected_boxplot: `r paste0("Divisive clustering_",as.character(params$input$selectFC[1]),"_vs_",as.character(params$input$selectFC[2]),"/GOI_boxplot.pdf")`

```{r, out.width="0.3\\linewidth", include=TRUE, fig.align="center", echo=FALSE}
if(!is.null(params$multi_boxplot_reactive) && length(params$input$selectFC) == 2 && !is.null(params$input$multi_pattern1_count_rows_selected)){
try(magick::image_read_pdf(paste0("Divisive clustering_",as.character(params$input$selectFC[1]),"_vs_",as.character(params$input$selectFC[2]),"/GOI_boxplot.pdf")))
}else print("Not performed")
```

 - Enrichment analysis 
 
 Gene_set: **`r params$input$Gene_set7`**
 
 dotplot: `r paste0("Divisive clustering_",as.character(params$input$selectFC[1]),"_vs_",as.character(params$input$selectFC[2]),"/dotplot_",params$input$Gene_set7,".pdf")` 
 
 selected_clusters for dotplot: **`r params$input$multi_whichGroup1_1`**
 
 cnet plot `r paste0("Divisive clustering_",as.character(params$input$selectFC[1]),"_vs_",as.character(params$input$selectFC[2]),"/cnet_",params$input$Gene_set7,".pdf")`
 
 selected_clusters for cnetplot: **`r params$input$multi_whichGroup1_2`**
 
 enrichment table: `r paste0("Divisive clustering_",as.character(params$input$selectFC[1]),"_vs_",as.character(params$input$selectFC[2]), "/dotplot_",params$input$Gene_set7,".txt")`

 
```{r, out.width="0.3\\linewidth", include=TRUE, fig.align="center", echo=FALSE}
if(!is.null(params$multi_boxplot_reactive) && length(params$input$selectFC) == 2 && !is.null(params$input$Gene_set7) && !is.null(params$input$multi_whichGroup1_1)){
try(magick::image_read_pdf(paste0("Divisive clustering_",as.character(params$input$selectFC[1]),"_vs_",as.character(params$input$selectFC[2]),"/dotplot_",params$input$Gene_set7,".pdf")))
}else print("Not performed")
```
```{r, out.width="0.3\\linewidth", include=TRUE, fig.align="center", echo=FALSE}
if(!is.null(params$multi_boxplot_reactive) && length(params$input$selectFC) == 2 && !is.null(params$input$Gene_set7) && !is.null(params$input$multi_whichGroup1_1) && params$input$multi_whichGroup1_2 != "not selected"){
try(magick::image_read_pdf(paste0("Divisive clustering_",as.character(params$input$selectFC[1]),"_vs_",as.character(params$input$selectFC[2]),"/cnet_",params$input$Gene_set7,".pdf")))
}else print("Not performed")
```
```{r echo = FALSE}
if(!is.null(params$multi_boxplot_reactive) && length(params$input$selectFC) == 2 && !is.null(params$input$Gene_set7) && !is.null(params$input$multi_whichGroup1_1)){
table <- params$multi_enrich_div_table[,-3:-8]
table$Group <- try(gsub("\n","",table$Group))
knitr::kable(table)
}
```

\newpage

## k-means clustering

 - Pair for fold change cut-off: 
**`r paste0(as.character(params$input$selectFC2[1]),"_vs_",as.character(params$input$selectFC2[2]))`**
 - Option: Pair for fold change cut-off: **`r paste0(as.character(params$input$selectFC2_2[1]),"_vs_",as.character(params$input$selectFC2_2[2]))`**
 - The DEG number after the filtration: **`r length(rownames(params$multi_deg_count1))`**
 - Tested gene number: 
```{r echo = FALSE, results='asis'}
num <- length(rownames(params$multi_deg_count1))
if(!is.null(num)){
  if(!is.null(params$input$topP2)){
    if(num < params$input$topP2) cat(paste0("**",num, "**\n\n")) else cat(paste0("**",params$input$topP2, "**\n\n"))
  }
}else print("Not performed")
```  

 - k-means number: **`r params$input$multi_kmeans_number`**

 Summary boxplot: `r paste0("kmeans clustering_",as.character(params$input$selectFC2[1]),"_vs_",as.character(params$input$selectFC2[2]),"/kmeans_boxplot.pdf")`
 
 Heatmap: `r paste0("kmeans clustering_",as.character(params$input$selectFC2[1]),"_vs_",as.character(params$input$selectFC2[2]),"/kmeans_heatmap.pdf")`

```{r, out.width="0.3\\linewidth", include=TRUE, fig.align="center", echo=FALSE}
if(!is.null(params$multi_kmeans_box) && length(params$input$selectFC2) == 2){
try(magick::image_read_pdf(paste0("kmeans clustering_",as.character(params$input$selectFC2[1]),"_vs_",as.character(params$input$selectFC2[2]),"/kmeans_boxplot.pdf")))
}else print("Not performed")
```
```{r, out.width="0.3\\linewidth", include=TRUE, fig.align="center", echo=FALSE}
if(!is.null(params$multi_kmeans_box) && length(params$input$selectFC2) == 2){
try(magick::image_read_pdf(paste0("kmeans clustering_",as.character(params$input$selectFC2[1]),"_vs_",as.character(params$input$selectFC2[2]),"/kmeans_heatmap.pdf")))
}else print("Not performed")
```

kmeans pattern file: `r paste0("kmeans clustering_",as.character(params$input$selectFC2[1]),"_vs_",as.character(params$input$selectFC2[2]),"/kmeans_pattern.txt")`

kmeans pattern count: `r paste0("kmeans clustering_",as.character(params$input$selectFC2[1]),"_vs_",as.character(params$input$selectFC2[2]),"/kmeans_pattern_norm_count_",params$input$multi_selectfile2,".txt")`

selected_boxplot: `r paste0("kmeans clustering_",as.character(params$input$selectFC2[1]),"_vs_",as.character(params$input$selectFC2[2]),"/GOI_boxplot.pdf")`
```{r, out.width="0.3\\linewidth", include=TRUE, fig.align="center", echo=FALSE}
if(!is.null(params$multi_kmeans_box) && length(params$input$selectFC2) == 2 && !is.null(params$input$multi_kmeans_count_table_rows_selected)){
try(magick::image_read_pdf(paste0("kmeans clustering_",as.character(params$input$selectFC2[1]),"_vs_",as.character(params$input$selectFC2[2]),"/GOI_boxplot.pdf")))
}else print("Not performed")
```

 - Enrichment analysis 

 Gene_set: **`r params$input$Gene_set8`**
 
 dotplot: `r paste0("kmeans clustering_",as.character(params$input$selectFC2[1]),"_vs_",as.character(params$input$selectFC2[2]),"/dotplot_",params$input$Gene_set8,".pdf")` 
 
 selected_clusters for dotplot: **`r params$input$multi_whichGroup2_1`**
 
 cnet plot `r paste0("kmeans clustering_",as.character(params$input$selectFC2[1]),"_vs_",as.character(params$input$selectFC2[2]),"/cnet_",params$input$Gene_set8,".pdf")`
 
 selected_clusters for cnetplot: **`r params$input$multi_whichGroup2_2`** 
 
 enrichment table: `r paste0("kmeans clustering_",as.character(params$input$selectFC2[1]),"_vs_",as.character(params$input$selectFC2[2]),"/enrichment_",params$input$Gene_set8,".txt")`
 
 
```{r, out.width="0.3\\linewidth", include=TRUE, fig.align="center", echo=FALSE}
if(!is.null(params$multi_kmeans_box) && length(params$input$selectFC2) == 2 && !is.null(params$input$Gene_set8) && !is.null(params$input$multi_whichGroup2_1)){
try(magick::image_read_pdf(paste0("kmeans clustering_",as.character(params$input$selectFC2[1]),"_vs_",as.character(params$input$selectFC2[2]),"/dotplot_",params$input$Gene_set8,".pdf")))
}else print("Not performed")
```
```{r, out.width="0.3\\linewidth", include=TRUE, fig.align="center", echo=FALSE}
if(!is.null(params$multi_kmeans_box) && length(params$input$selectFC2) == 2 && !is.null(params$input$Gene_set8) && !is.null(params$input$multi_whichGroup2_1) && params$input$multi_whichGroup2_2 != "not selected"){
try(magick::image_read_pdf(paste0("kmeans clustering_",as.character(params$input$selectFC2[1]),"_vs_",as.character(params$input$selectFC2[2]),"/cnet_",params$input$Gene_set8,".pdf")))
}else print("Not performed")
```
```{r echo = FALSE}
if(!is.null(params$multi_kmeans_box) && length(params$input$selectFC2) == 2 && !is.null(params$input$Gene_set8) && !is.null(params$input$multi_whichGroup2_1)){
table <- params$multi_enrich_k_table[,-3:-8]
table$Group <- try(gsub("\n","",table$Group))
knitr::kable(table)
}
```

\newpage

## GSEA

 - Pair for GSEA: **`r params$input$selectEnrich_pair`**
 - Gene set: **`r params$input$Gene_set6`**
 
 GSEA plot: `r paste0("GSEA/GSEA_",params$input$Gene_set6,".pdf")`
 
 GSEA table: `r paste0("GSEA/GSEA_",params$input$Gene_set6,".txt")`
 
```{r, out.width="0.3\\linewidth", include=TRUE, fig.align="center", echo=FALSE}
if(!is.null(params$multi_GSEA_table) && length(params$input$selectEnrich_pair) == 2 && params$input$Species6 != "not selected"){
try(magick::image_read_pdf(paste0("GSEA/GSEA_",params$input$Gene_set6,".pdf")))
}else print("Not performed")
```
```{r echo = FALSE}
if(!is.null(params$multi_GSEA_table) && length(params$input$selectEnrich_pair) == 2 && params$input$Species6 != "not selected"){
table <- try(params$multi_GSEA_table[,-2:-4])
table <- try(table[,-3])
try(knitr::kable(table[,-5:-7]))
}
```



\newpage

## Citation

 - Etoh K. & Nakao M. A web-based integrative transcriptome analysis, RNAseqChef, uncovers cell/tissue type-dependent action of sulforaphane. JBC, 2023, in press. https://doi.org/10.1016/j.jbc.2023.104810