---
title: "Pair-wise DEG with RNAseqChef v1.0.8"
date: '`r format(Sys.time(), "%y/%m/%d %H:%M")`'
params:
    raw_count: [some object]
    input: [some object]
    norm_count: [some object]
    deg_norm_count: [some object]
    data_degcount: [some object]
    data_degcount2: [some object]
    enrichment_enricher: [some object]
    enrichment_1_gsea: [some object]
    pair_enrich_table: [some object]
    pair_gsea_table: [some object]
    metadata: [some object]
output:
  word_document
fontsize: 10pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Parameters
 - Uploaded file name:
 
```{r echo = FALSE, results='asis'}
if(params$input$data_file_type == "Row1" && !is.null(params$input$file3)) {
  try(cat(paste0("raw_count_data: **", params$input$file3$name,"**\n\n")))
}
if(params$input$data_file_type == "Row2" && !is.null(params$input$file1)) {
  try(cat(paste0("raw_count_data: **", params$input$file1$name,"**\n\n")))
}
```

```{r echo = FALSE, results='asis'}
if(params$input$data_file_type == "Row2" && !is.null(params$input$file2)) {
  try(cat(paste0("metadata: **",params$input$file2$name,"**\n\n")))
  try(knitr::kable(params$metadata))
  cat("\n\n")
}
```
  
 
 - Experimental condition: 
 **`r unique(gsub("\\_.+$", "", colnames(params$raw_count)))[1]` vs `r unique(gsub("\\_.+$", "", colnames(params$raw_count)))[2]`**
 - Method for DEG detection: 
 **`r params$input$DEG_method`**
  - Method for FDR control: 
 **`r params$input$FDR_method`**
 - Species: 
 **`r params$input$Species`**
```{r echo = FALSE, results='asis'}
if(sum(is.element(no_orgDb, params$input$Species)) == 1){
  try(cat(paste0("\nOrtholog: **", params$input$Ortholog,"**\n\n")))
  try(cat(paste0("Host: **", params$input$Biomart_archive,"**\n\n")))
}
```

 - Cut-off condition: 
 FoldChange = **`r params$input$fc`**, FDR = **`r params$input$fdr`**, 
 Basemean = **`r params$input$basemean`**
 - tested raw count data
```{r echo = FALSE}
knitr::kable(head(params$raw_count))
```

 - Option: uploaded normalized count data: 
```{r echo = FALSE}
if(!is.null(params$input$norm_file1)){
  knitr::kable(head(params$norm_count))
}else print("no upload")
```

\newpage

##  Result overview

 - Clustering analysis (PCA, MDA, dendrogram (ward. D2)) (Clustering/clustering.pdf)

```{r, out.width="0.3\\linewidth", include=TRUE, fig.align="center", echo=FALSE}
try(magick::image_read_pdf("./Clustering/clustering.pdf"))
```

 - MA-plot and heatmap (DEG_result/MAplot.pdf)
 
```{r, out.width="0.3\\linewidth", include=TRUE, fig.align="center", echo=FALSE}
try(magick::image_read_pdf("./DEG_result/MAplot.pdf"))
```

 - table data
    - DEG_result (DEG_result/DEG_result.txt)
    - DEG_count_up (DEG_result/up.txt)
    - DEG_count_down (DEG_result/down.txt)
    - Normalized_count_data (DEG_result/normalized_count.txt)
    - PCA_table (Clustering/pca.txt)

\newpage

##  GOI (Genes of interest) profiling

 - Volcano plot (GOI_profiling/volcano_plot.pdf) and heatmap (GOI_profiling/heatmap.pdf)

```{r, out.height=255.68181, out.width=255.68181, include=TRUE, fig.align="center", echo=FALSE}
if(!is.null(params$input$xrange) && !is.null(params$input$yrange)){
try(magick::image_read_pdf("./GOI_profiling/volcano_plot.pdf"))
    }else print("Not performed")
```
```{r, out.height=255.68181, out.width=178.977267, include=TRUE, fig.align="center", echo=FALSE}
if(!is.null(params$input$xrange) && !is.null(params$input$yrange)){
try(magick::image_read_pdf("./GOI_profiling/heatmap.pdf"))
    }else print("Not performed")
```

 - Boxplot (GOI_profiling/boxplot.pdf)
 
```{r, out.width="0.3\\linewidth", include=TRUE, fig.align="center", echo=FALSE}
if(!is.null(params$input$xrange) && !is.null(params$input$yrange)){
try(magick::image_read_pdf("./GOI_profiling/boxplot.pdf"))    
    }else print("Not performed")
```

\newpage

## Enrichment analysis

 - Gene set: 
 **`r params$input$Gene_set`**
 
 - Plot (Enrichment_analysis/Enrichment_analysis_`r params$input$Gene_set`.pdf)
```{r, out.width="0.3\\linewidth", include=TRUE, fig.align="center", echo=FALSE}
if(!is.null(params$input$Gene_set) && params$input$Species != "not selected"){
try(magick::image_read_pdf(paste0("Enrichment_analysis/Enrichment_analysis_",params$input$Gene_set,".pdf")))      
    }else print("Not performed")
```

Enrichment result table (Enrichment_analysis/GSEA_`r params$input$Gene_set`.txt)

```{r echo = FALSE}
if(!is.null(params$input$Gene_set) && params$input$Species != "not selected"){
table <- params$pair_enrich_table[,-3:-8]
knitr::kable(table)
}
```

GSEA result table (Enrichment_analysis/Enrichment_analysis_`r params$input$Gene_set`.txt)

```{r echo = FALSE}
if(!is.null(params$input$Gene_set) && params$input$Species != "not selected"){
table <- params$pair_gsea_table[,-2:-4]
table <- table[,-3]
knitr::kable(table[,-5:-7])
}
```

\newpage

## Citation

 - Etoh K. & Nakao M. A web-based integrative transcriptome analysis, RNAseqChef, uncovers cell/tissue type-dependent action of sulforaphane. JBC, 2023, in press. https://doi.org/10.1016/j.jbc.2023.104810